---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bis620.2022

<!-- badges: start -->
[![R-CMD-check](https://github.com/Gladys-Wang/bis620.2022/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Gladys-Wang/bis620.2022/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/Gladys-Wang/bis620.2022/branch/main/graph/badge.svg)](https://app.codecov.io/gh/Gladys-Wang/bis620.2022?branch=main)
[![Test coverage](https://github.com/Gladys-Wang/bis620.2022/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/Gladys-Wang/bis620.2022/actions/workflows/test-coverage.yaml)
[![Lint](https://github.com/Gladys-Wang/bis620.2022/actions/workflows/lint.yaml/badge.svg)](https://github.com/Gladys-Wang/bis620.2022/actions/workflows/lint.yaml)
<!-- badges: end -->

## Installation

You can install the development version of bis620.2022 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Gladys-Wang/bis620.2022")
```

# Description
The goal of bis620.2022 is to incorporate several packages so that you could invoke them in R and also from github. 

The accel_plot is a function to generate plots of time series data with time or frequency on the x-axis. You could implement it by calling:
```{r example}
library(bis620.2022)
data(ukb_accel)
accel_plot(ukb_accel[1:1000,])
```
The spectral_signature is a function that generates a dataframe by adding a frequency column to time series data. You could implement it by calling:
```{r}
data(ukb_accel)
spectral_signature(ukb_accel[1:1000,])
```
